---
title: "Practice Presentations"
format: revealjs
---

## ABOUT DATA
These brief presentations about data will allow you to exercise your R and git skills with collaborators, use the following structure to organize your report.  


```{r, echo = TRUE}
# Displays code in slides

```

```{r, eval = TRUE, echo = FALSE}
# Run code, do not display code

```

```{r, eval = FALSE, echo = TRUE}
# Display code, DO NOT run code

```


## Summary Stats (Calculations)
What are all the variables?
Which variables may be predictors/outcomes?
How are the variables distributed?

```{r}

```

## Summary Stats (Graphics)
Use boxplots to check for outliers. Eliminate entries outside of the fence.
Use histogram to further explore variable distributions.
```{r, fig.align='center'}
# ALIGN your figures to the center of the slide

```


## Relationships
Normalize your variables, which variables are correlated, are any of your variables co-linear.


```{r, eval = T, echo = F}

```

## Visualization or Analysis

```{r}

```

## Visualization or Analysis

```{r}

```
